RCloud: Integrating Exploratory Visualization, Analysis and Deployment

### 2014-02-13 paper.tex
abstract I wrote for an upcoming talk

%% Abstract section.
\abstract{
} % end of abstract

>>>>

%% Abstract section.
\abstract{ Consider the emerging role of a data science team within an
  organization. Different data scientists and statisticians usually
  work on loosely related problems, and transition fluidly from
  exploratory data analysis to automated diagnostics and reports,
  which need to be deployed for wider consumption on the
  organization. There are two problems with the current
  practice. First, there is a gap in this workflow: EDA is performed
  with one set of tools, and automated reports and deployments with
  another. Second, current EDA environments mostly assume a
  single-developer perspective, while data scientist teams could
  greatly benefit from easier sharing of scripts, beyond that which a
  traditional version control system can provide. In this paper, we
  will present RCloud, a system designed to enable collaborative data
  analysis, visualization and deployment on the web. We will discuss
  the design decisions, tradeoffs and limitations, and compare it to
  current proposals.
} % end of abstract
